%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {DiDi Research America, LLC.} % Organization
    {Mountain View, CA, USA} % Location
    {Oct. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Develop and deploy tools and pipeline in the area of intelligent driving on vehicles to improve the driving quality and make it smarter and safer.}
      \item {Research and implement the state of the art algorithms, adapt them into driving scenarios and make it running real-time on cars.}
      \item {Collaborate with third-party car companies and other groups to deliver the intelligent vehicles.}
      \item {Contribute to Company’s intellectual property through patent filing.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Metropia, Inc.} % Organization
    {Tucson, Arizona USA} % Location
    {Dec. 2017 - Oct. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Work closely with data science team to transform
    research prototypes into production level code.}
       \item {Design and build the scalable backend system that provides end users
    with real time and predictive multi-modal travel options via web
    API. Main stack: Python 3, PostgreSQL, Sklearn, Django, Django Rest Framework,
    Redis, Celery and Pytest.}
       \item {Scale out existing systems to handle high loads.}
       \item {Deploy and monitor backend services on AWS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\textbf{Research Assistant} for \href{https://www.noao.edu/ANTARES/}{ANTARES} project} % Job title
    {University of Arizona} % Organization
    {Tucson, Arizona USA} % Location
    {Aug. 2014 - Aug. 2015, Aug. 2016 - Mar. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed and implemented Python API for astronomical
    alert data manipulation, using MySQL as DB backend.}
      \item {Built the provenance data view system using Django and MySQL.}
      \item {Worked on various components of ANTARES system,
    including data injection, alert simulator and alert packet format specification.}
        \item {Managed the dedicated CentOS cluster; designed and
    built the autoconfiguration and bootstrap 
    system using Puppet and Vagrant.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\textbf{Teaching Assistant} for CS460: Database Systems}
    {University of Arizona} % Organization
    {Tucson, Arizona USA} % Location
    {Fall 2015 \& Spring 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created solutions for programming and written assignments.}
        \item {Created tutorials and demo for the final course project ``Database-driven Web
    Application'' using Oracle, Tomcat and JSP, mentored project teams.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\textbf{Research Assistant} for
    \href{http://imsure.github.io/NeuralGiraph/}{Neural Modeling in
    Hadoop} project}
    {University of St. Thomas} % Organization
    {St. Paul, Minnesota USA} % Location
    {Aug. 2013 - May. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed a new design pattern for graph algorithms in
    MapReduce and implemented a large scale neural network
    model in MapReduce.}
      \item {Re-implemented the model with a vertex-centric approach
    using Apache Giraph and resulted in 60\% performance improvement.}
      \item
    {Published
    (\href{https://ieeexplore.ieee.org/document/6871824/}{Link to paper})
    and presented
    (\href{https://www.slideshare.net/imsure/ieee-eittalklargescaleneuralmodelinginmap-reducegiraph}{link
    to slides})
    a paper as first author in an IEEE regional conference.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {Danfoss Power Solutions} % Organization
    {Plymouth, Minnesota USA} % Location
    {June. 2012 - May. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Migrated the legacy software (written in C) to the new hardware
    platform with other team members and conducted unit testing.}
       \item {Improved overall software quality using static code analyzer FlexeLint, identified
    and corrected several vulnerabilities existed in the legacy code.}
           \item {Built a tool (in Python) for summarizing, indexing and
    querying large volume of warning messages produced by FlexeLint.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Embedded Software Engineer \& Training Assistant} % Job title
    {Beijing Farsight Technology and Information} % Organization
    {Beijing, China} % Location
    {July. 2009 - July. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Linux device drivers and applications (in C) for various ARM
    platforms (ARM 9, 11 \& Cortex-A8).}
        \item {Prepared training materials and instructed trainees in
    their lab sessions and final design project.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Platomix Technologies. (Start-up company)} % Organization
    {Beijing, China} % Location
    {Feb. 2009 - July. 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Joined the team that built the initial prototype for
    Samsung's Remote Test Lab (RTL).}
       \item {Developed a multi-threaded program (in C++) for RTL
    device (Linux smartphone) to handle requests from RTL clients.}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
