%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Academic Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\textbf{Research Assistant} with Dr. Richard Snodgrass on \href{https://www.noao.edu/ANTARES/}{ANTARES} project} % Job title
    {University of Arizona} % Organization
    {Tucson, Arizona USA} % Location
    {Aug. 2016 - Mar. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Chief programmer of ANTARES (The Arizona-NOAO Temporal
    Analysis and Response to Events System) project.} 
        \item {Deployed ANTARES system to the dedicated CentOS
    cluster using MySQL Cluster as Database backend.}
        \item {Analyzed and improved the performance of ANTARES data
    processing pipeline.}
        \item {Designed and proposed the data provenance framework for
    ANTARES to answer provenance questions that astronomers would ask.}
        \item {Designed the packet format specification for alert data
        and implemented the simulator for generating alert streams.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\textbf{Research Assistant} with Dr. Richard Snodgrass on \href{https://www.noao.edu/ANTARES/}{ANTARES} project} % Job title
    {University of Arizona} % Organization
    {Tucson, Arizona USA} % Location
    {Aug. 2014 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented the database used by ANTARES,
    as well as the web front-end for querying data produced by ANTARES
    pipeline using Django and MySQL.} 
        \item {Collaborated with astronomers to design, implement
    and document the Python API for astronomical alert data manipulation.}
        \item {Designed and built the bootstrapping
    system to run ANTARES pipeline in a pseudo-distributed mode
    using Vagrant and Puppet.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\textbf{Independent Study} with Dr. Beichuan Zhang
    on \href{https://named-data.net/}{Named Data Networking} (NDN) project} % Job title
    {University of Arizona} % Organization
    {Tucson, Arizona USA} % Location
    {Spring 2016 \& Fall 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched consumer-driven congestion control mechanisms in
    NDN.}
        \item {Implemented TCP-like congestion control algorithms in NDN
    consumer (in C++), specifically, TCP RENO, CUBIC and VEGAS.
    Evaluated and studied the performance of each of them in the
    context of NDN.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {\textbf{Teaching Assistant} with Dr. Lester McCann
    on CS460: Database Systems}
    {University of Arizona} % Organization
    {Tucson, Arizona USA} % Location
    {Fall 2015 \& Spring 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Held office hours; graded programming and written
    assignments; prepared solutions for written assignments.}
        \item {Designed the final project ``Database-driven Web
    Application'' using Oracle, Tomcat and JSP; evaluated
    students' design and implementation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\textbf{Student Researcher} with Dr. Brad Rubin and Dr. Jadin Jackson}
    {University of St. Thomas} % Organization
    {St. Paul, Minnesota USA} % Location
    {Aug. 2013 - May. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {We initiated the project ``Large-scale Neural Network
    Modeling with Hadoop'' to explore the use of big data technologies in
    computational neuroscience and I was responsible for investigating 
    graph processing in Hadoop.}
        \item {Implemented the neural network with MapReduce model in
    Hadoop.}
        \item {Implemented the neural network with vertex-centric model
    using Apache Giraph in Hadoop.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
