%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\textbf{Research Assistant} with Dr. Richard Snodgrass on \href{https://www.noao.edu/ANTARES/}{ANTARES} project} % Job title
    {University of Arizona} % Organization
    {Tucson, Arizona USA} % Location
    {Aug. 2014 - Aug. 2015, Aug. 2016 - Mar. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed and implemented the Python API for astronomical
    alert data manipulation, using MySQL as DB backend.}
      \item {Worked on various components of ANTARES system,
    including data injection, alert simulator and alert packet format specification.}
        \item {Managed the dedicated CentOS cluster; designed and
    built the autoconfiguration and bootstrap 
    system using Puppet and Vagrant.}
        \item {Analyzed and improved the performance of ANTARES data
    processing pipeline; researched data provenance.}
        \item {Designed the data provenance framework for
    ANTARES to answer provenance questions that astronomers would ask.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\textbf{Independent Study} with Dr. Beichuan Zhang
    on \href{https://named-data.net/}{Named Data Networking} (NDN) project} % Job title
    {University of Arizona} % Organization
    {Tucson, Arizona USA} % Location
    {Spring 2016 \& Fall 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched consumer-driven congestion control mechanisms in
    NDN.}
        \item {Implemented TCP-like congestion control algorithms in NDN
    consumer (in C++), specifically, TCP RENO, CUBIC and VEGAS.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {\textbf{Teaching Assistant} with Dr. Lester McCann
    on CS460: Database Systems}
    {University of Arizona} % Organization
    {Tucson, Arizona USA} % Location
    {Fall 2015 \& Spring 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Held office hours; graded programming and written
    assignments; prepared solutions for written assignments.}
        \item {Designed the final project ``Database-driven Web
    Application'' using Oracle, Tomcat and JSP; evaluated
    students' design and implementation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\textbf{Student Researcher} with Dr. Brad Rubin and Dr. Jadin
    Jackson on project: \href{http://imsure.github.io/NeuralGiraph/}{Neural
    Modeling in Hadoop}}
    {University of St. Thomas} % Organization
    {St. Paul, Minnesota USA} % Location
    {Aug. 2013 - May. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Researched graph processing in Hadoop; proposed an
    improved graph algorithm design pattern in MapReduce.}
      \item {Implemented a large scale basal ganglia neural network
    model in MapReduce.}
      \item {Implemented the model
       with Apache Giraph, improved
    performance by 60\% compared to the MapReduce implementation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {Danfoss Power Solutions} % Organization
    {Plymouth, Minnesota USA} % Location
    {June. 2012 - May. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Migrated the legacy software to the new hardware
    platform with other team members and conducted unit testing.}
       \item {Built a backend tool (in Python) for indexing and
    querying large volume of messages produced by static code analyzer FlexeLint.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Platomix Technologies. (Start-up company)} % Organization
    {Beijing, China} % Location
    {Feb. 2009 - July. 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for the
    development on RTL device, which was part of the initial prototype for
    Samsung's Remote Test Lab (RTL).}
       \item {Implemented the communication protocol (in C++) between RTL device (
    LiMo platform) and RTL proxy.}
       \item {Developed a daemon process (in C++) for RTL
    device to handles requests from proxy, in order for RTL client
    to remotely control the device.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
