%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {Danfoss Power Solutions} % Organization
    {Plymouth, Minnesota USA} % Location
    {June. 2012 - May. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Migrated the legacy software to the new hardware
    platform with other team members and conducted unit testing.}
       \item {Applied static code analyer FlexeLint to
    the legacy software written in C.}
       \item {Built a tool (in Python) for summarizing, indexing and
    querying large volume of warning messages produced by FlexeLint.}
       \item {Improved overall software quality, identified
    and corrected several vulnerabilities existed in the legacy code.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Embedded Software Engineer \& Training Assistant} % Job title
    {Beijing Farsight Technology and Information} % Organization
    {Beijing, China} % Location
    {July. 2009 - July. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Linux device drivers and applications (in C) for various ARM
    platforms (ARM 9, 11 \& Cortex-A8).}
        \item {Assisted training instructors in preparing training
    content and developed technical how-to documents for ARM and
    Embedded Linux training.}
        \item {Instructed trainees in their lab sessions and final design project.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Platomix Technologies. (Start-up company)} % Organization
    {Beijing, China} % Location
    {Feb. 2009 - July. 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Being part of a team that built the initial prototype for
    Samsung's Remote Test Lab (RTL), I was responsible for the
    development on RTL device.}
       \item {Implemented the communication protocol between RTL device (
    LiMo platform) and RTL proxy.}
       \item {Developed a daemon process (in C++) for RTL
    device to handles requests from proxy, in order for RTL client
    to remotely control the device.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
