%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Selected Coursework}

\cvsubsection{University of Arizona}

\begin{cventries}

%---------------------------------------------------------
  \cvcoursework
    {Database Systems Implementation (CS560)
    - \href{http://research.cs.wisc.edu/coral/mini_doc/minibase.html}{Minibase}} % Job title
    {Spring 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on a team of two, we developed core components
    for Minibase to make it function correctly.}
       \item {Implemented Heap File, Buffer Manager and B$^+$ Tree in C++.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cvcoursework
    {Principles of Computer Networking (CS525) - Virtual Router}
    {Fall 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a virtual router in C that runs PWOSPF routing protocol
    and routes real IP packets.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cvcoursework
    {Principles of Compilation (CS553) - C- - Compiler}
    {Spring 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented code generator for C- - (a subset
    of C) compiler in C that converts abstract syntax tree (AST) into
    MIPS assembly code.}
        \item {Implemented various O1, O2 and O3 optimizations.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cvcoursework
    {Parallel and Distributed Programming (CS522) - MPI Profiler \& Redundant MPI}
    {Fall 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a profiler (in C) for MPI that generates a
    critical-path profile for MPI programs.}
        \item {Implemented the redundant MPI protocol (in C) by which
    an MPI program runs redundantly such that if one MPI rank fails,
    the program will continue with the replica rank.}
      \end{cvitems}
    }
%---------------------------------------------------------

\end{cventries}

\cvsubsection{University of St. Thomas}

\begin{cventries}

%---------------------------------------------------------
  \cvcoursework
    {Big Data Architecture (SEIS736) - Design patterns for graph algorithms in MapReduce}
    {Fall 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched design patterns for graph algorithms in MapReduce.}
        \item {Developed an improved design pattern to
    avoid writing entire graph structure onto disk when the graph
    structure remains unchanged during processing.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cvcoursework
    {Data Visualization (SEIS785) - Who's going to win 2013 NBA
    Championship ?}
    {Spring 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed ETL process to pull NBA datasets from
    multiple sources into a data warehouse using Python and SQLite.}
        \item {Visualized and analyzed data to explore what are the
    key factors that make a championship team using R.}
      \end{cvitems}
    }
%---------------------------------------------------------

  \cvcoursework
    {Information Retrieval (SEIS731) - Shakespeare Search Engine}
    {Fall 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a search engine from scratch in Python for
    Shakespeare's whole collection, including a web crawler, an
    indexer and a query processor.} % description
    \item {The indexer supports both inverted index and positional
    index and the query processor supports both free text queries and
    phrase queries.}
      \end{cvitems}
    }
%---------------------------------------------------------

\end{cventries}
