%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Metropia, Inc.} % Organization
    {Tucson, Arizona USA} % Location
    {Dec. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Build robust, lasting, and scalable web service based
    software products which support Metropia’s routing,
    prediction, and payment modules.}
       \item {Perform code reviews and ensure exceptional code quality.}
       \item {Evaluate the technical tradeoffs of every decision.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\textbf{Research Assistant} for \href{https://www.noao.edu/ANTARES/}{ANTARES} project} % Job title
    {University of Arizona} % Organization
    {Tucson, Arizona USA} % Location
    {Aug. 2014 - Aug. 2015, Aug. 2016 - Mar. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed and implemented Python API for astronomical
    alert data manipulation, using MySQL as DB backend.}
      \item {Built the provenance data view system with Django and MySQL.}
      \item {Worked on various components of ANTARES system,
    including data injection, alert simulator and alert packet format specification.}
        \item {Managed the dedicated CentOS cluster; designed and
    built the autoconfiguration and bootstrap 
    system using Puppet and Vagrant.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\textbf{Teaching Assistant} for CS460: Database Systems}
    {University of Arizona} % Organization
    {Tucson, Arizona USA} % Location
    {Fall 2015 \& Spring 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Held office hours; graded programming and written
    assignments; prepared solutions for written assignments.}
        \item {Designed and evaluated final course project ``Database-driven Web
    Application'' using Oracle, Tomcat and JSP.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\textbf{Student Researcher} for
    \href{http://imsure.github.io/NeuralGiraph/}{Neural Modeling in
    Hadoop} project}
    {University of St. Thomas} % Organization
    {St. Paul, Minnesota USA} % Location
    {Aug. 2013 - May. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed a new design pattern for graph algorithms in
    MapReduce and implemented a large scale neural network
    model in MapReduce.}
      \item {Re-implemented the model
       with Apache Giraph (made use of vertex-centric in memory computation), improved
    performance by 60\% compared to the MapReduce implementation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {Danfoss Power Solutions} % Organization
    {Plymouth, Minnesota USA} % Location
    {June. 2012 - May. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Migrated the legacy software (written in C) to the new hardware
    platform with other team members and conducted unit testing.}
       \item {Improved overall software quality using static code analyzer FlexeLint, identified
    and corrected several vulnerabilities existed in the legacy code.}
           \item {Built a tool (in Python) for summarizing, indexing and
    querying large volume of warning messages produced by FlexeLint.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Embedded Software Engineer \& Training Assistant} % Job title
    {Beijing Farsight Technology and Information} % Organization
    {Beijing, China} % Location
    {July. 2009 - July. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Linux device drivers and applications (in C) for various ARM
    platforms (ARM 9, 11 \& Cortex-A8).}
        \item {Prepared training materials and instructed trainees in
    their lab sessions and final design project.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Platomix Technologies. (Start-up company)} % Organization
    {Beijing, China} % Location
    {Feb. 2009 - July. 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Joined the team that built the initial prototype for
    Samsung's Remote Test Lab (RTL).}
       \item {Developed a multi-threaded program (in C++) for RTL
    device (Linux smartphone) to handle requests from RTL clients.}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
